\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-27 manuscript.Rmd
test the push
Just added a line to the rmd to test the push function
Manuscript updated

```{r CFA 23 items, include=FALSE}
LB.cfa <- read_excel("recoded not reversed_CFA.xlsx")
LB.model.Cor <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item41+ item7 + item27 + item21
            F5 =~ item19 + item34 + item2"

>>>>

```{r CFA 23 items, include=FALSE}
LB.cfa <- read_excel("recoded not reversed_CFA.xlsx")
LB.model.Cor <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item41+ item7 + item27 + item21
            F5 =~ item19 + item34 + item2" 
# all items
